dads manual

### 2023-03-29 inst/gitbook/07_specific_examples.Rmd
manual big update
Updated numbering in gitbook
typos

@@

# Changing branch length when reaching n taxa {#EG_modify_brlen}

@@

## Founding event: a generating a subtree with no fossils {#EG_founding_purebirth}

@@

## Founding event: a generating a subtree a different process {#EG_founding_traits}

>>>>

# Specific examples

@@

## Changing branch length when reaching n taxa {#EG_modify_brlen}

@@

## Founding event: generating a subtree with no fossils {#EG_founding_purebirth}

@@

## Founding event: generating a subtree a different process {#EG_founding_traits}

### 2023-03-29 inst/gitbook/index.Rmd
Updated numbering in gitbook
typos

The first section `Getting started` is aimed for people with a `R` beginner level:
 * you know what a package is - and how to install it;
 * you know what a function is - and what arguments are;
 * you have already (vaguely) heard that they are different types of objects in R - like matrices (`"matrix"`) or trees (`"phylo"`);
 * and you have already looked for documentation and bugs online.

The sections after that are a bit more advanced and requires the following level:
 * you have already created functions before;
 * you know how to subset elements of a list - i.e. you understand the `list$element` syntax;
 * you are aware that both `TRUE == 1` and `FALSE == 0` are `TRUE`;
 * you have heard that the objects in R have classes and that it sometimes matters - for example you know that R can differentiate between `as.numeric(1)` and `as.integer(1)`;
 * you owe part of your life to Stack Overflow.

@@

# The birth-death algorithm {#bdalgorithm}

>>>>

The first section `Getting started` is aimed for people with a `R` beginner level:

 * you know what a package is - and how to install it;
 * you know what a function is - and what arguments are;
 * you have already (vaguely) heard that they are different types of objects in R - like matrices (`"matrix"`) or trees (`"phylo"`);
 * and you have already looked for documentation and bugs online.

The sections after that are a bit more advanced and requires the following level:

 * you have already created functions before;
 * you know how to subset elements of a list - i.e. you understand the `list$element` syntax;
 * you are aware that both `TRUE == 1` and `FALSE == 0` are `TRUE`;
 * you have heard that the objects in R have classes and that it sometimes matters - for example you know that R can differentiate between `as.numeric(1)` and `as.integer(1)`;
 * you owe part of your life to Stack Overflow.

@@

## The birth-death algorithm {#bdalgorithm}
